LCS Tool: A Computational Platform for Lagrangian Coherent Structures

### 2014-12-02 main.tex
Correct overfull warnings
Update demo script names

\begin{figure}
\begin{center}
\setlength\figurewidth{.4\textwidth}
\input{graphics/double_gyre/poincare_return_map.tikz}
\end{center}
\caption{Example of a Poincare map obtained for an elliptic LCS. The abscissa, $s$, represents distance along Poincare section. The ordinate, $p(s) - s$, represents distance of Poincare orbit return point from initial position. Circle markers indicate closed orbit positions. The filled circle indicates the outermost fixed point of the Poincare map, marking the intersection of a coherent Lagrangian vortex boundary with the Poincare section.}
\label{f:Poincare return map}
\end{figure}

@@

\lstinputlisting[caption={LCS Tool commands for double gyre elliptic LCSs. Subset of the LCS Tool script \lstinline!demo/double_gyre/hyperbolic_shear_lcs.m!},
                 label=l:double gyre elliptic LCS]{listings/double_gyre/elliptic_lcs_subset.m}

@@

% FIXME Reviewer #5, comment #4: There is too much source code in the main content such as cref{l:double gyre lambda strain stretch LCS,l:Bickley jet elliptic hyperbolic LCS subset,l:ocean data elliptic hyperbolic lcs}. They could be arranged as an appendix at the end.
\lstinputlisting[
        caption={LCS Tool commands for double gyre hyperbolic LCSs. Subset of the LCS Tool script \lstinline!demo/double_gyre/hyperbolic_shear_lcs.m!},
        label=l:double gyre lambda strain stretch LCS]
        {listings/double_gyre/hyperbolic_lcs_subset.m}

@@

\lstinputlisting[
        caption={LCS Tool commands for Bickley jet elliptic and hyperbolic LCSs. Subset of the LCS Tool script \lstinline!demo/bickley_jet/hyperbolic_shear_lcs.m!},
        label=l:Bickley jet elliptic hyperbolic LCS subset]
        {listings/bickley_jet/elliptic_hyperbolic_lcs_subset.m}

\begin{figure}
\centering
\setlength\figurewidth{.35\textwidth}
\import{graphics/bickley_jet/}{elliptic_repelling_lcs_details.tikz}
\import{graphics/bickley_jet/}{elliptic_attracting_lcs_details.tikz}
\caption{
LCSs in the Bickley jet.
Resolution is $500 \times 200$.
Elliptic LCSs are green, shrink line LCSs are red and stretch line LCSs are blue.
White dots indicate $\lambda_2$ maxima for shrink lines and $\lambda_1$ minima stretch lines.
FTLE shown in the background.
$\lambda$ values of elliptic LCSs from left to right are [0.95,\,0.80,\,0.94,\,0.80,\,0.94], $\lambda \in [0.80,1.20]$, $\Delta\lambda = 0.01$.
}
\label{f:Bickley jet LCS}
\end{figure}

@@

The data is given at a spatial resolution of $1/4\degree$ and a temporal resolution of 7 days.
Due to the discrete data, defining the right hand side of \cref{eq:dtlon} and \cref{eq:dtlat} involves spline interpolation in space and time.
An interpolant is generated first, then the function \lstinline!flowdata_derivative! evaluates the interpolants for the zonal and meridional velocity at the needed coordinates.
\Cref{l:ocean data elliptic hyperbolic lcs} shows the relevant part of the code in LCS Tool's ocean demo file \lstinline!demo/ocean_dataset/hyperbolic_shear_lcs.m!.
The commands for the interpolation of the velocity data are given in \crefrange{ll:interpolation start}{ll:interpolation end}.

\lstinputlisting[
        caption={LCS Tool commands for ocean data elliptic and hyperbolic LCSs. Subset of the LCS Tool script \lstinline!demo/ocean_dataset/hyperbolic_shear_lcs.m!},
        label={l:ocean data elliptic hyperbolic lcs}]
        {listings/ocean_dataset/elliptic_hyperbolic_lcs_subset.m}

@@

\Cref{f:ocean dataset LCS} shows elliptic and hyperbolic LCSs on 22 November 2006, the same time as analysed in \citet{haller13:_coher_lagran,haller14:_adden_coher_lagran,beron-vera13:_objec_agulh}.
In those references, the integration time is 90 days.
We use a shorter time to avoid tangling hyperbolic LCSs.
Our analysis via LCS Tool reveals five coherent eddies.
The largest, at $(3,-32)$, has a non-stretching boundary, i.e., $\lambda = 1$.
It corresponds to eddy \#2 in figure~3 of \citet{beron-vera13:_objec_agulh}.
Four additional smaller coherent eddies are found.
They do not stay coherent over 90 days.
The hyperbolic LCSs determine the deformation of the fluid between coherent eddies.

\begin{figure}
\begin{center}
\setlength\figurewidth{.4\textwidth}
\import{graphics/ocean_dataset/}{elliptic_repelling_lcs.tikz}
\import{graphics/ocean_dataset/}{elliptic_attracting_lcs.tikz}
\end{center}
\caption{
LCSs in the ocean velocity data from satellite altimetry.
Resolution is $400 \times 400$.
Elliptic LCSs are green, shrink line LCSs are red and stretch line LCSs are blue.
White dots indicate $\lambda_2$ maxima for shrink lines and $\lambda_1$ minima stretch lines.
FTLE shown in the background.
$\lambda = 1.00, 1.08, 0.94, 0.90, 1.06$.
}
\label{f:ocean dataset LCS}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\setlength\figurewidth{.35\textwidth}
\input{graphics/double_gyre/poincare_return_map.tikz}
\end{center}
\caption{Example of a Poincare map obtained for an elliptic LCS. The abscissa, $s$, represents distance along Poincare section. The ordinate, $p(s) - s$, represents distance of Poincare orbit return point from initial position. Circle markers indicate closed orbit positions. The filled circle indicates the outermost fixed point of the Poincare map, marking the intersection of a coherent Lagrangian vortex boundary with the Poincare section.}
\label{f:Poincare return map}
\end{figure}

@@

\lstinputlisting[caption={LCS Tool commands for double gyre elliptic LCSs. Subset of the LCS Tool script \lstinline!demo/double_gyre/elliptic_hyperbolic_lcs.m!},
                 label=l:double gyre elliptic LCS]{listings/double_gyre/elliptic_lcs_subset.m}

@@

% FIXME Reviewer #5, comment #4: There is too much source code in the main content such as cref{l:double gyre lambda strain stretch LCS,l:Bickley jet elliptic hyperbolic LCS subset,l:ocean data elliptic hyperbolic lcs}. They could be arranged as an appendix at the end.
\lstinputlisting[
        caption={LCS Tool commands for double gyre hyperbolic LCSs. Subset of the LCS Tool script \lstinline!demo/double_gyre/elliptic_hyperbolic_lcs.m!},
        label=l:double gyre lambda strain stretch LCS]
        {listings/double_gyre/hyperbolic_lcs_subset.m}

@@

\lstinputlisting[
        caption={LCS Tool commands for Bickley jet elliptic and hyperbolic LCSs. Subset of the LCS Tool script \lstinline!demo/bickley_jet/elliptic_hyperbolic_lcs.m!},
        label=l:Bickley jet elliptic hyperbolic LCS subset]
        {listings/bickley_jet/elliptic_hyperbolic_lcs_subset.m}

\begin{figure}
\centering
\setlength\figurewidth{.325\textwidth}
\import{graphics/bickley_jet/}{elliptic_repelling_lcs_details.tikz}
\import{graphics/bickley_jet/}{elliptic_attracting_lcs_details.tikz}
\caption{
LCSs in the Bickley jet.
Resolution is $500 \times 200$.
Elliptic LCSs are green, shrink line LCSs are red and stretch line LCSs are blue.
White dots indicate $\lambda_2$ maxima for shrink lines and $\lambda_1$ minima stretch lines.
FTLE shown in the background.
$\lambda$ values of elliptic LCSs from left to right are [0.95,\,0.80,\,0.94,\,0.80,\,0.94], $\lambda \in [0.80,1.20]$, $\Delta\lambda = 0.01$.
}
\label{f:Bickley jet LCS}
\end{figure}

@@

The data is given at a spatial resolution of $1/4\degree$ and a temporal resolution of 7 days.
Due to the discrete data, defining the right hand side of \cref{eq:dtlon} and \cref{eq:dtlat} involves spline interpolation in space and time.
An interpolant is generated first, then the function \lstinline!flowdata_derivative! evaluates the interpolants for the zonal and meridional velocity at the needed coordinates.
\Cref{l:ocean data elliptic hyperbolic lcs} shows the relevant part of the code in LCS Tool's ocean demo file \lstinline!demo/ocean_dataset/elliptic_hyperbolic_lcs.m!.
The commands for the interpolation of the velocity data are given in \crefrange{ll:interpolation start}{ll:interpolation end}.

\lstinputlisting[
        caption={LCS Tool commands for ocean data elliptic and hyperbolic LCSs. Subset of the LCS Tool script \lstinline!demo/ocean_dataset/elliptic_hyperbolic_lcs.m!},
        label={l:ocean data elliptic hyperbolic lcs}]
        {listings/ocean_dataset/elliptic_hyperbolic_lcs_subset.m}

@@

\begin{sloppypar}
\Cref{f:ocean dataset LCS} shows elliptic and hyperbolic LCSs on 22 November 2006, the same time as analysed in \citet{haller13:_coher_lagran,haller14:_adden_coher_lagran,beron-vera13:_objec_agulh}.
In those references, the integration time is 90 days.
We use a shorter time to avoid tangling hyperbolic LCSs.
Our analysis via LCS Tool reveals five coherent eddies.
The largest, at $(3,-32)$, has a non-stretching boundary, i.e., $\lambda = 1$.
It corresponds to eddy \#2 in figure~3 of \citet{beron-vera13:_objec_agulh}.
Four additional smaller coherent eddies are found.
They do not stay coherent over 90 days.
The hyperbolic LCSs determine the deformation of the fluid between coherent eddies.
\end{sloppypar}

\begin{figure}
\begin{center}
\setlength\figurewidth{.375\textwidth}
\import{graphics/ocean_dataset/}{elliptic_repelling_lcs.tikz}
\import{graphics/ocean_dataset/}{elliptic_attracting_lcs.tikz}
\end{center}
\caption{
LCSs in the ocean velocity data from satellite altimetry.
Resolution is $400 \times 400$.
Elliptic LCSs are green, shrink line LCSs are red and stretch line LCSs are blue.
White dots indicate $\lambda_2$ maxima for shrink lines and $\lambda_1$ minima stretch lines.
FTLE shown in the background.
$\lambda = 1.00, 1.08, 0.94, 0.90, 1.06$.
}
\label{f:ocean dataset LCS}
\end{figure}
